UCD\\MSc Thesis Proposal:\\\emph{An Approach To Continuous Capacity Planning In Cloud Environment With Uptime Based Pricing Model}

### 2014-06-30 paper/proposal.tex
wording

New IaaS solutions are becoming available with a growing number of supported pricing models. This makes the offering attractive enough to move the entire businesses to the Cloud. The availability of different pricing schemes based on resource utilisation and uptime reveals new challenges in already unpredictive capacity planning process. Is it better to pay some amount of money upfront and less hourly rate? Is is better to invest in less heavy utilized instances or maybe in more medium ones? When exactly one pricing scheme becomes more cost effective?

@@

  \begin{itemize}
  \item Mandatory:
    \begin{itemize}
      \item A formal definition of continous capacity planning approach.
      \item A design of an algorithm that calculates an uptime optimality factor of VM utilisation based on a pricing scheme.
    \end{itemize}

@@

  \item Exceptional
    \begin{itemize}
      \item Generate suggestions to change the configuration based on the calculated results.
    \end{itemize}

>>>>

New IaaS solutions are becoming available with a growing number of supported pricing models. More often than not, a hosted Cloud environment is used to design and build an infrastructure for a product. The recent availability of different pricing schemes based on resource utilisation and uptime reveals new challenges in already unpredictive capacity planning process. 
When exactly does one pricing scheme becomes more cost effective?

@@

\begin{itemize}
\item Mandatory:
\begin{itemize}
\item A definition of continous capacity planning approach.
\item A design of an algorithm that calculates VM utilisation optimality factor based on a pricing scheme.
\end{itemize}

@@

\item Exceptional
\begin{itemize}
\item Suggestions generation to change the configuration based on the calculated results.
\item An improvement to the algorithm that considers expotential discounting to help to make a cost effective choice over time.
\item Calculate trends based on historical data and suggest and an optimal configuration for this prediction.
\end{itemize}
